Experimenting with n-grams in Civil Procedure Codes

### 2014-08-04 experiment.Rmd
Added KWIC function

>>>>

It sure would be nice to be able to take an n-gram that we know is a match and to find the context in two codes. I'm going to assume that you've found a interesting match elsewhere, probably using the `compare_codes_by_shared_ngrams()` function, and want to investigate it further. This function takes the n-gram as a string and the two codes to look for it in. (Technically, I suppose, we're just implementing a generic search function.)

```{r}
kwic_ngram_match <- function(ngram, code_1, code_2, disp_chars = 100) {
  require(stringr)
  # The fixed() function from stringr indicates that we are using literal
  # characters rather than a regex.
  match_code_1 <- str_locate_all(code_1, fixed(ngram))[[1]]
  match_code_2 <- str_locate_all(code_2, fixed(ngram))[[1]]

  match_code_1[,1] <- match_code_1[,1] - disp_chars
  match_code_1[,2] <- match_code_1[,2] + disp_chars
  match_code_2[,1] <- match_code_2[,1] - disp_chars
  match_code_2[,2] <- match_code_2[,2] + disp_chars

  extract_code_1 <- str_sub(code_1, match_code_1[,1], match_code_1[,2])
  extract_code_2 <- str_sub(code_2, match_code_2[,1], match_code_2[,2])

  data.frame(ngram = ngram,
             orig_code = extract_code_1,
             dest_code = extract_code_2)
}
```
